    \documentclass[11pt]{letter}
    
    \textwidth=6.25in
    \textheight=9.2in
    \footskip=0.5in
    \oddsidemargin=0in
    \topmargin=-0.75in
    
    \usepackage{url}
    \usepackage{verbatim}
    \usepackage{amsmath}
    \usepackage{amssymb}
	\usepackage{cmbright}
	\usepackage{multicol}
	\usepackage{eurosym}
	\usepackage{graphicx}
	\usepackage{qrcode}

    
    \begin{document}
    
    \begin{center}
    
{\Huge\bf  Steven M. Wise}

{\Large\bf  Curriculum Vitae}

\qrcode{https://stevenmwise.github.io}

\url{swise1@utk.edu}  $\bigstar$  \url{https://faculty.utk.edu/Steven.Wise}
	\
\url{https://stevenmwise.github.io}  $\bigstar$    \url{https://github.com/stevenmwise}
	\\
\url{stevenmwise@gmail.com}  $\bigstar$   \url{https://scholar.google.com/citations?user=dGv7Ou8AAAAJ}
	\\
\url{https://www.researchgate.net/profile/Steven-Wise-5}
	\\
\url{https://orcid.org/0000-0003-3824-2075}
    \end{center}

    \medskip

{\LARGE\bf  Current Appointment}
    \begin{description}
    \item
Mathematics Department, University of Tennessee
	\begin{description}
	\item
\textbf{Professor}, August 2017 -- present
	\item
\textbf{Interim Department Head}, January 2020
	\item
\textbf{Associate Professor}, August 2012 -- July 2017
	\item
\textbf{Assistant Professor}, August 2007 -- July 2012
	\end{description}
	\end{description}
	
	\smallskip
	
{\LARGE\bf  Research Impact}
    \begin{description}
    \item
\textbf{Web of Science Highly Cited Researcher:} Mathematics, 2020, 2022
	\\
\url{https://recognition.webofscience.com/awards/highly-cited/2020/}
	\\
\url{https://recognition.webofscience.com/awards/highly-cited/2022/}
   	\item
\textbf{Google Scholar Citation Metrics:} about 8300 citations, h-index 47, as of March 2023
    \end{description}
    
    \smallskip
	
{\LARGE\bf  Research Interests}
    \begin{description}
    \item
\textbf{Computational Mathematics and Numerical Analysis:}~Approximation methods for nonlinear parabolic/hyperbolic PDE; convex-concave decomposition methods for bistable gradient equations. Multilevel pre-conditioners. Fast nonlinear solvers. Efficient adaptive multigrid methods for interface problems; methods for moving boundary problems, especially phase-field and diffuse interface methods. Rigorous stability and convergence of finite difference, finite element, pseudo-spectral and discontinuous galerkin methods for nonlinear and nonlocal, elliptic and parabolic PDE.
	\item
\textbf{Optimization:} Preconditioned Nesterov and multilevel methods for constrained and unconstrained optimization problems, especially those related to the discretization of nonlinear PDE and Calculus of Variations problems.

	\item
\textbf{Mathematical Biology:}~Modeling tissue growth and remodeling -- including cancerous tumor growth -- angiogenesis, and cancer treatment; spatiotemporal pattern formation in biological systems, morphogenesis.  Deformation, decomposition, and motion of biological membranes in viscous flows.
	\item
\textbf{Computational Materials Science:}~Growth and coarsening dynamics of heteroepitaxial thin films, long-time and large-scale coarsening of material microstructures, quantum dot formation, phase field crystal models, nonlocal models of phase transformation, crystal growth with strong interfacial anisotropy, elastically mediated phase transformations. Soft materials.
	\item
\textbf{Computational Fluid Dynamics:}~Phase field methods for two-phase flows with large density difference. Two-phase flows in porous media. Microstructural evolution of multiphase polymer systems, especially for organic photovoltaic (OPV) devices. Transport of ions in solution.
	\item
\textbf{Nonlinear PDE:}~Existence, uniqueness, and regularity of solutions for nonlinear parabolic-hyperbolic PDE and related integro-partial differential equations (IPDE), especially for models related to phenomena described above.
	\item
\textbf{Nonlinear Analysis:}~$\Gamma$ convergence and asymptotic analysis for diffuse interface problems.
    \end{description}

	
{\LARGE\bf Current Funding}
    \begin{description}
    
    \item
\textbf{NSF Grant, DMS-2012634:}~PI, {\sl Collaborative Research:  Efficient, Accurate, and Structure-Preserving Numerical Methods for Phase Field-Type Models with Applications,} \$200,000, 8/20 -- 7/23.

    \item
\textbf{ORNL-DOE-UT-Battelle CW24420:}~PI, {\sl BGK Kinetic Equations,} \$250,200, 1/22 -- 7/24. ORNL Technical Point of Contact: Ryan Glasby, \url{glasbyrs@ornl.gov}.
    
    \end{description}
    
 
{\LARGE\bf Previous Funding, Support, and Awards}
    \begin{description} 
    
    \item
\textbf{LANL-ORNL-DOE-UT-Battelle RFP584197:}~co-PI, {\sl Developing a better understanding of adaptive velocity grids for kinetic equations,} approx.~\$60,000, 2/20 -- 5/21. DOE-LANL Technical Point of Contact: Jeff Haack. (Originally funded at about \$640K, before budget cuts.)
 
    \item
\textbf{ORNL-DOE-UT-Battelle 3400267345:}~PI, {\sl Quadratic Unconstrained Binary Optimization and Regularized Problems Expressed via Steady States of Dynamical Systems,} \$40,506, 6/18 -- 8/18. ORNL Technical Point of Contact: Ryan Bennink.
    
%    \item
%\textbf{(Pending) NSF Grant, DMS-1814463:}~co-PI, {\sl Development of Mathematical Analysis and Optimal Control Theory to Understand Biology Models,} \$318,711, 8/18 -- 7/21.
    
%    \item
%\textbf{(Pending) NSF-Simons Research Center Grant:}~co-PI, {\sl Emergence in Mathematical Biology Across Scales (EMBAS) Center,}  more than \$1,000,000, multi-year.
    
    \item
\textbf{ORNL-DOE-UT-Battelle 3400253096:}~PI, {\sl Physics-Based, Self-Consistent Simulation of Neutron Reflectivity for Thin Films of Block Copolymers with Incorporated Nanoparticles,} \$138,834, 7/17 -- 9/18. ORNL Technical Points of Contact: Rajeev Kumar, Valeria Lauter, Bobby Sumpter.

    \item
\textbf{Dresden Fellowship:} Technische Universit\"{a}t Dresden, Germany,  \EUR{10,500}, 9/1/17 -- 11/30/17.
    
    \item
\textbf{ORNL-DOE-UT-Battelle Subcontract 3400252731:}~PI, {\sl Modeling and Simulation of Ion Transport in Polymer Systems and Novel Discrete Ordinate Methods for Modeling Radiation Transport via Kinetic Equations,} \$60,285, 6/17 -- 5/18. ORNL Technical Point of Contact: Cory Hauck. 


%    \item
%\textbf{(Pending) NSF Grant, DMS-1664624:}~PI, {\sl FRG: Collaborative Research: Variational Models of Membrane Network Dynamics,} \$327,220, 8/17 -- 7/20. Lead-PI: Keith Promislow (MSU), PI: YongCheng Zhou (CSU).

    \item
\textbf{IMA Conference Grant:}~co-PI, {\sl The 2017 Barrett Lectures: the Mathematical Foundations of Data Science,} \$5,000, 4/17 -- 3/18.


    \item
\textbf{NSF Grant, DMS-1719854:}~PI, {\sl Efficient, Adaptive, and Convergent Numerical Methods for Phase Field Equations with Applications,} \$200,000, 8/17 -- 11/21.


	 \item
\textbf{NSF Grant, DMS-1700494:}~co-PI, {\sl The 2017 Barrett Lectures: the Mathematical Foundations of Data Science,} \$16,000, 4/17 -- 3/18.

    \item
\textbf{NSF Grant, DMS-1418692:}~PI, {\sl Efficient, Adaptive, and Convergent Numerical Methods for Phase Field and Phase Field Crystal Equations with Applications,} \$105,000, 9/14 -- 8/18.

    \item
\textbf{NSF Grant, DMS-1338314:}~co-PI, {\sl Southeastern-Atlantic Regional Conference on Differential Equations 2013,} \$21,938.00, 8/13 -- 4/14.

    \item
\textbf{NSF Grant, DMS-1115390:}~Lead PI, {\sl Collaborative Research: Stable and Efficient Convexity-Splitting Schemes for Bistable Gradient PDEs,} \$160,000, 7/11 -- 6/14.

    \item
\textbf{NSF Grant, DMS-0818030:}~PI, {\sl Collaborative Research: Multiscale Modeling of Solid Tumor Growth,} \$70,000, 9/08 -- 8/11.
	
	\item
\textbf{Workshop Support:}~Lead Organizer, {\sl Investigative Workshop: Solid Tumor Modeling}, National Institute for Mathematical and Biological Synthesis (NIMBioS), approx.~40 participants, 1/19/11 -- 1/21/11.
%\newline\url{http://www.nimbios.org/workshops/WS_tumor_modeling.html}
	
	\item
\textbf{Mid-Career Faculty Research Achievement Award:} College or Arts and Sciences, University of Tennessee, Fall 2014 Convocation, \$500.
	\item
\textbf{Junior Faculty Research Achievement Award:} College or Arts and Sciences, University of Tennessee, Fall 2010 Convocation, \$1000.
	\item
\textbf{Best Graduate Teaching Award:} Mathematics Department, University of Tennessee, 2012-13, and 2013-14.
	\item
\textbf{Best Graduate Advising Award:} Mathematics Department, University of Tennessee, 2016-17.

    \end{description}
	
	\smallskip
	
{\LARGE\bf Support and Awards for PhD Students}
    \begin{description}
    \item
John Cummings, United States Department of Energy Office of Science Graduate Student Research (SCGSR) Program Award/Fellowship, \$36,000 (approx.), 1/15 -- 1/16. PhD 2017.  Topic:~``Simulating Polymer-Solvent Mixtures for Organic-Photovoltaic Devices." Co-advisors R.~Kumar (ORNL), \textbf{S.M.~Wise} (UTK).
    \item
Kylie Berry, United States Department of Energy Office of Science Graduate Student Research (SCGSR) Program Award/Fellowship, \$18,000 (approx.), 1/19 -- 6/19. PhD 2019.  Topic:~``Energy-based blending for local-nonlocal coupling in linear elasticity." Advisors P.~Seleson (ORNL), Tadele Mengesha (UTK), and \textbf{S.M.~Wise} (UTK).
	\end{description}
	
	\smallskip
  
{\LARGE\bf  University Education}
    \begin{description}
    \item
\textbf{Ph.D.,}~University of Virginia, Engineering Physics; May 2003.
    \begin{description}
    \item
Advisor: W.C.~Johnson
    \item
Dissertation: ``Diffuse Interface Model for Microstructural Evolution of Stressed, Binary Thin Films on Patterned Substrates."
    \end{description}
    \item
 \textbf{Graduate Studies,} Virginia Tech and Penn State, Mathematics; August 1996--December 1998.
    \begin{description}
    \item
Coursework: Analysis (Real, Complex, Functional, and Numerical), Applied Mathematics.
    \end{description}
    \item
\textbf{B.S.,}~Clarion University of Pennsylvania, Mathematics; May
1996.
    \begin{description}
    \item
Minor (Coursework Equivalent): Physics
    \end{description}
    \end{description}
	
	\smallskip
  
{\LARGE\bf  Professional Membership}
    \begin{description}
    \item
 \textbf{Society for Industrial and Applied Mathematics (SIAM)}
    \begin{description}
    \item
Activity Group: Mathematical Aspects of Materials Science
    \end{description}
    \end{description}
	
	\smallskip

{\LARGE\bf  Prior and Visiting Appointments}
    \begin{description}    \item 
\textbf{Dresden Senior Fellow,} Technische Universit\"{a}t Dresden, September 2017 -- November 2017.
    \item 
\textbf{Visiting Associate Researcher,} University of California, Irvine,
Mathematics Department, March 2015 -- June 2015. 
    \item 
\textbf{Visiting Assistant Professor,} University of California, Irvine,
Mathematics Department, July 2006 -- July 2007.
    \item 
\textbf{Post-Doctoral Researcher,} University of California, Irvine, Mathematics Department, July 2004 -- June 2006.
    \begin{description}
    \item
Advisor: John S. Lowengrub
    \end{description}
    	\item 
\textbf{Post-Doctoral Researcher,} University of California, Irvine, Biomedical Engineering and Mathematics Departments, March 2003 -- June 2004.
    \begin{description}
    \item
Advisors: John S. Lowengrub and Vittorio Cristini
    \end{description}
	\item
\textbf{Research Assistant,} University of Virginia, Engineering Physics Program, August 1999 -- March 2003.
    \item
\textbf{Scientist,} United States Navy, NSWC-Dahlgren (Dahlgren,Virginia), January 1999 -- August 1999.
    \item
\textbf{Teaching Assistant--Primary Instructor,} Penn State, Mathematics Department, August 1998 -- December 1998.
    \item
\textbf{Research Assistant,} Virginia Tech, Mathematics Department, May 1997 -- August 1998.
    \item
\textbf{Teaching Assistant,} Virginia Tech, Mathematics Department, August 1996 -- April 1997.
    \end{description}


{\LARGE\bf  Textbooks and Research Monographs}
    \begin{enumerate}
    \item
A.J.~Salgado and \textbf{S.M.~Wise}, {\sl Classical Numerical Analysis: A Comprehensive Course}, Cambridge University Press, September 2022, 937 pages.
	\\
\url{https://www.cambridge.org/9781108837705}
	\\
\url{https://doi.org/10.1017/9781108942607}
    \end{enumerate}



{\LARGE\bf  Journal Publications}
    \begin{enumerate}
%    \item
%D.~Schaal and \textbf{S.M.~Wise}, {\sl Rado Numbers for Some Inequalities and an Arbitrary Number of Colors}, Proceedings of the Twenty-seventh Southeastern International Conference on Combinatorics (Baton Rouge, LA, 1996), Congr.~Numer.~121 (1996), 147-153.

    \item
D.~Schaal and \textbf{S.M.~Wise}, {\sl Rado Numbers for Some Inequalities and an Arbitrary Number of Colors}, Congr.~Numer.~121 (1996), 147-153.

    \item
\textbf{S.M.~Wise}, A.J.~Sommese, and L.T.~Watson, {\sl Algorithm 801: POLSYS\_PLP: A Partitioned Linear Product Homotopy Code for Solving Polynomial Systems of Equations}, ACM TOMS 26 (2000) 176-200.
	\\
\url{https://doi.org/10.1145/347837.347885}

    \item
W.C.~Johnson, P.H.~Leo, Y.~Zhen, and \textbf{S.M.~Wise}, {\sl Spinodal Decomposition in Thin Plates Subjected to a Temperature Gradient}, Modeling the Performance of Engineering Structural Materials II (TMS Fall 2001 Meeting), (2001).

    \item
\textbf{S.M.~Wise} and W.C.~Johnson, {\sl Competitive Phase Growth in Stressed Thin Films}, Modeling the Performance of Engineering Structural Materials II (TMS Fall 2001 Meeting), (2001).

    \item
W.C.~Johnson and \textbf{S.M.~Wise}, {\sl Phase Decomposition of a Binary Thin Film on a Patterned Substrate}, Appl.~Phys.~Lettr.~81 (2002), 919-921.
	\\
\url{https://doi.org/10.1063/1.1497193}

    \item
W.C.~Johnson, \textbf{S.M.~Wise}, J.Y.~Huh, and J.~Favergeon, {\sl Effect of Interfacial Segregation on Phase Decomposition of a Thin Film on a Patterned Substrate}, Met.~Mater.~Int.~9 (2003) 1-8.
	\\
\url{https://doi.org/10.1007/BF03027222}

    \item
\textbf{S.M.~Wise} and W.C.~Johnson, {\sl Numerical Simulations of Pattern-Directed Phase Decomposition in a Stressed, Binary Thin Film}, J.~Appl.~Phys.~94 (2003) 889-898.
	\\
\url{https://doi.org/10.1063/1.1577230}

    \item
\textbf{S.M.~Wise}, J.S.~Kim, and W.C.~Johnson, {\sl Surface-Directed Spinodal Decomposition in a Stressed Two-Dimensional Thin Film}, Thin Solid Films 473 (2004) 151-163.
	\\
\url{https://doi.org/10.1016/j.tsf.2004.07.075}

    \item
\textbf{S.M.~Wise}, J.S.~Lowengrub, J.S.~Kim, and W.C.~Johnson, {\sl Efficient Phase-Field Simulation of Quantum Dot Formation in a Strained Heteroepitaxial Film}, Superlattices and Microstructures 36 (2004) 293-304.
	\\
\url{https://doi.org/10.1016/j.spmi.2004.08.029}

    \item
J.S.~Lowengrub, Z.~Hu, \textbf{S.M.~Wise}, J.S.~Kim, and A.~Voigt, {\sl Phase-Field Modeling of Step Dynamics}, MRS Proceedings, 859E (2005) JJ8.6.1-JJ8.6.6.

    \item
X.~Zheng, \textbf{S.M.~Wise}, and V.~Cristini, {\sl Nonlinear Simulation of Tumor Necrosis, Neo-Vascularization and Tissue Invasion via an Adaptive Finite-Element/Level-Set Method}, Bull.~Math.~Biol.~67 (2005) 211-259.
	\\
\url{https://doi.org/10.1016/j.bulm.2004.08.001}

    \item
\textbf{S.M.~Wise}, J.S.~Lowengrub, J.S.~Kim, K.~Thornton, P.~Voorhees, and W.C.~Johnson, {\sl Quantum Dot Formation on a Strain-Patterned Epitaxial Thin Film}, Appl.~Phys.~Lettr.~87 (2005) 133102.
	\\
\url{https://doi.org/10.1063/1.2061852}

	\item
J.~Favergeon, J.Y.~Huh, W.C.~Johnson, and \textbf{S.M.~Wise}, {\sl Wetting Transitions in a Binary Thin Film}, Met.~Mater.~Int.~11 (2005) 487-497.
	\\
\url{https://doi.org/10.1007/BF03027499}

    \item
H.B.~Frieboes, J.S.~Lowengrub, \textbf{S.M.~Wise}, X.~Zheng, P.~Macklin, E.L.~Bearer, and V.~Cristini, {\sl Computer Simulation of Glioma Growth and Morphology}, NeuroImage  37 (2007) S59-S70.
	\\
\url{https://doi.org/10.1016/j.neuroimage.2007.03.008}

    \item
\textbf{S.M.~Wise}, J.S.~Kim, and J.S.~Lowengrub, {\sl Solving the Regularized, Strongly Anisotropic Cahn-Hilliard Equation by an Adaptive Nonlinear Multigrid Method}, J.~Comput.~Phys.~226 (2007) 414-446.
	\\
\url{https://doi.org/10.1016/j.jcp.2007.04.020}

	\item
S.~Torabi, \textbf{S.M.~Wise}, J.S.~Lowengrub, A.~Ratz, and A.~Voigt, {\sl A New Method for Simulating Strongly Anisotropic Cahn-Hilliard Equations}, MS\&T 2007 Conference Proceedings (2007) 1432-1444.	

	\item
Z.~Hu, S.~Li, J.S.~Lowengrub, \textbf{S.M.~Wise}, and A.~Voigt, {\sl Phase Field Modeling of Nanoscale Island Dynamics}, TMS 2008 (137th annual meeting) Supplemental Proceedings: Materials Processing and Properties (2008) 111-116.

	\item
V.~Cristini, H.B.~Frieboes, X.~Li, J.S.~Lowengrub, P.~Macklin, S.~Sanga, \textbf{S.M.~Wise}, and X.~Zheng, {\sl Nonlinear Modeling and Simulation of Tumor Growth, in N. Bellomo, M. Chaplain, and E. De Angelis (Editors), ``Selected Topics in Cancer Modeling: Genesis, Evolution, Immune Competition, and Therapy,"}  Birkhauser (2008) 1-69.
	\\
\url{https://doi.org/10.1007/978-0-8176-4713-1_6}

	\item
S.~Torabi, \textbf{S.M.~Wise}, S.~Li, A.~Voigt, J.S.~Lowengrub, and P.~Zhou, {\sl Simulations of Nonlinear Strongly Anisotropic, Misfitting Crystals and Thin Films}, MRS Proceedings~1087 (2008) 1087-V02-01. 
	\\
\url{https://doi.org/10.1557/PROC-1087-V02-01}

	\item
\textbf{S.M.~Wise}, J.S.~Lowengrub, H.B.~Frieboes, and V.~Cristini, {\sl Three-Dimensional Multispecies Nonlinear Tumor Growth--I: Model and Numerical Method}, J.~Theor.~Biol.~253 (2008) 524-543.
	\\
\url{https://doi.org/10.1016/j.jtbi.2008.03.027}

	\item
V.~Cristini, X.~Li, J.S.~Lowengrub, and \textbf{S.M.~Wise}, {\sl Nonlinear Simulations of Solid Tumor Growth using a Mixture Model: Invasion and Branching}, J.~Math.~Biol.~58 (2009) 723-763.
	\\
\url{https://doi.org/10.1007/s00285-008-0215-x}

	\item
S.~Torabi, J.S.~Lowengrub, A.~Voigt, and \textbf{S.M.~Wise}, {\sl A New Phase-Field Model for Strongly Anisotropic Systems}, Proc.~R.~Soc.~A 465 (2009) 1337-1359.
	\\
\url{https://doi.org/10.1098/rspa.2008.0385}


	\item
E.L.~Bearer, J.S.~Lowengrub, H.B.~Frieboes, Y.L.~Chuang, F.~Jin, \textbf{S.M.~Wise}, M.~Ferrari, D.B.~Agus, and V.~Cristini, {\sl Multiparameter Computational Modeling of Tumor Invasion}, Cancer Res.~69 (2009) 4493-4501.
	\\
\url{https://doi.org/10.1158/0008-5472.CAN-08-3834}

	\item
J.S.~Lowengrub, V.~Cristini, H.B.~Frieboes, X.~Li, P.~Macklin, S.~Sanga, \textbf{S.M.~Wise}, and X.~Zheng, {\sl Lecture Notes on Nonlinear Tumor Growth: Modeling and Simulation, in  B.C.~Khoo, Z.~Li, and P.~Lin (Editors) ``Interface Problems and Methods in Biological and Physical Flows,"} World Scientific (2009) 69-133.
	\\
\url{https://doi.org/10.1142/9789812837851_0002}

	\item
\textbf{S.M.~Wise}, C.~Wang, and J.S.~Lowengrub, {\sl An Energy Stable and Convergent Finite Difference Scheme for the Phase Field Crystal Equation}, SIAM J.~Numer.~Anal.~47 (2009) 2269-2288.
	\\
\url{https://doi.org/10.1137/080738143}

	\item
Z.~Hu, \textbf{S.M.~Wise}, C.~Wang, and J.S.~Lowengrub, {\sl Stable Finite Difference, Nonlinear Multigrid Simulation of the Phase Field Crystal Equation}, J.~Comput.~Phys.~228 (2009) 5323-5339.
	\\
\url{https://doi.org/10.1016/j.jcp.2009.04.020}

	\item
P.~Zhou, J.S.~Lowengrub, and \textbf{S.M.~Wise}, {\sl Coarsening of 3D Thin Films Under the Influence of Strong Surface Anisotropy and Elastic Stresses}, TMS 2009 (138th annual meeting), Supplemental Proceedings: Materials Characterization, Computation and Modeling (2009) 39-46.
	\\
\url{https://apps.dtic.mil/dtic/tr/fulltext/u2/a538820.pdf}

	\item
J.S.~Lowengrub, H.B.~Frieboes, F.~Jin, Y.L.~Chuang, X.~Li, P.~Macklin, \textbf{S.M.~Wise}, and V.~Cristini, {\sl Nonlinear Modeling of Cancer: Bridging the Gap Between Cells and Tumors}, Nonlinearity 23 (2010) R1-R91.
	\\
\url{https://doi.org/10.1088/0951-7715/23/1/R01}

	\item
C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl Unconditionally Stable Schemes for Equations of Thin Film Epitaxy}, Discrete Contin. Dyn. Syst. Ser. A 28 (2010) 405-423.
	\\
\url{https://doi.org/10.3934/dcds.2010.28.405}

    \item
\textbf{S.M.~Wise}, {\sl Unconditionally Stable Finite Difference, Nonlinear Multigrid Simulation of the Cahn-Hilliard-Hele-Shaw System of Equations}, J.~Sci.~Comput. 44 (2010) 38-68.
	\\
\url{https://doi.org/10.1007/s10915-010-9363-4}
	\item
H.B.~Frieboes, F.~Jin, Y.L.~Chuang, \textbf{S.M.~Wise}, J.S.~Lowengrub, and V.~Cristini, {\sl Three-Dimensional Multispecies Nonlinear Tumor Growth--II: Angiogenesis and Tissue Invasion}, J. Theor.~Biol.~264 (2010) 1254-1278.
	\\
\url{https://doi.org/10.1016/j.jtbi.2010.02.036}

	\item
Y.L.~Chuang, F.~Jin, and \textbf{S.M.~Wise}, {\sl Numerical Schemes, in V.~Cristini and J.S.~Lowengrub (Authors), ``Multiscale Modeling of Cancer: An Integrated Experimental and Mathematical Modeling Approach,"} Cambridge University Press (2010) 153-182.
	\\
\url{https://dx.doi.org/10.1017/CBO9780511781452.009}

	\item
C.~Wang and \textbf{S.M.~Wise}, {\sl Global Smooth Solutions of the Three-Dimensional Modified Phase Field Crystal Equation}, Methods Appl.~Anal.~17 (2010) 191-212.
	\\
\url{https://dx.doi.org/10.4310/MAA.2010.v17.n2.a4}

    \item
\textbf{S.M.~Wise}, J.S.~Lowengrub, and V.~Cristini, {\sl An Adaptive Algorithm for Simulating Solid Tumor Growth using Mixture Models}, Math.~Comput.~Model.~53 (2011) 1-20.
	\\
\url{https://doi.org/10.1016/j.mcm.2010.07.007}
 
	\item
C.~Wang and \textbf{S.M.~Wise}, {\sl An Energy Stable and Convergent Finite Difference Scheme for the Modified Phase Field Crystal Equation}, SIAM J.~Numer.~Anal.~49 (2011) 945-969.
	\\
\url{https://doi.org/10.1137/090752675}

	\item
Z.~Hu, J.S.~Lowengrub, \textbf{S.M.~Wise}, and A.~Voigt, {\sl Phase-Field Modeling of Epitaxial Growth: Applications to Step Trains and Island Dynamics}, Physica D 241 (2012) 77-94.
	\\
\url{https://doi.org/10.1016/j.physd.2011.09.004}

	\item
J.~Shen, C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl Second-Order Convex Splitting Schemes for Gradient Flows with Ehrlich-Schwoebel Type Energy: Application to Thin Film Epitaxy}, SIAM J.~Numer.~Anal.~50 (2012) 105-125.
	\\
\url{https://doi.org/10.1137/110822839}
    
    \item
X.~Feng and \textbf{S.M.~Wise}, {\sl Analysis of a Darcy-Cahn-Hilliard Diffuse Interface Model for the Hele-Shaw Flow and its Fully Discrete Finite Element Approximation}, SIAM J.~Numer.~Anal.~50 (2012) 1320-1343.
	\\
\url{https://doi.org/10.1137/110827119}

    \item
P.~Zhou, \textbf{S.M.~Wise}, X.~Li, and J.S.~Lowengrub, {\sl Coarsening of Elastically Stressed, Strongly Anisotropic Driven Thin Films}, Phys.~Rev.~E 85 (2012) 061605.
	\\
\url{https://doi.org/10.1103/PhysRevE.85.061605}

	\item
W.~Chen, S.~Conde, C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl A Linear Energy Stable Scheme for a Thin Film Model without Slope Selection}, J.~Sci.~Comput.~52 (2012) 546-562.
	\\
\url{https://doi.org/10.1007/s10915-011-9559-2}

    \item
C.~Collins, J.~Shen, and \textbf{S.M.~Wise}, {\sl An Efficient, Energy Stable Scheme for the Cahn-Hilliard-Brinkman System}, Commun.~Comput.~Phys.~13 (2013) 929-957.
	\\
\url{https://doi.org/10.4208/cicp.171211.130412a}

    \item
A.~Baskaran, Z.~Hu, J.S.~Lowengrub, C.~Wang, \textbf{S.M.~Wise}, and P.~Zhou, {\sl Energy Stable and Efficient Finite-Difference Nonlinear-Multigrid Schemes for the Modified Phase Field Crystal Equation}, J.~Comput.~Phys.~250 (2013) 270-292.
	\\
\url{https://doi.org/10.1016/j.jcp.2013.04.024}

	\item
A.~Aristotelous, O.~Karakashian, \textbf{S.M.~Wise}, {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for a Modified Cahn-Hilliard Equation and an Efficient Nonlinear Multigrid Solver}, Discrete Cont. Dyn. Syst. B 18 (2013) 2211-2238.
	\\
\url{https://doi.org/10.3934/dcdsb.2013.18.2211}

    \item
A.~Baskaran, J.S.~Lowengrub, C.~Wang, and \textbf{S.M.~Wise}, {\sl Convergence of a Second Order Convex Splitting Scheme for the Modified Phase Field Crystal Equation}, SIAM J.~Numer.~Anal.~51 (2013) 2851-2873.
	\\
\url{https://doi.org/10.1137/120880677}

    \item
W.~Chen, C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl A Linear Iteration Algorithm for an Energy Stable Second Order Scheme for a Thin Film Model Without Slope Selection}, J.~Sci.~Comput.~59 (2014) 574-601.
	\\
\url{https://doi.org/10.1007/s10915-013-9774-0}

    \item
Y.~Chen, \textbf{S.M.~Wise}, V.B.~Shenoy, and J.S.~Lowengrub, {\sl A Stable Scheme for a Nonlinear, Multispecies Tumor Growth Model with an Elastic Membrane}, Int.~J.~Numer.~Meth.~Biomed.~Engng.~30 (2014) 726-754.
	\\ 
\url{https://doi.org/10.1002/cnm.2624}

	\item
Z.~Guan, J.S.~Lowengrub, C.~Wang, and \textbf{S.M.~Wise}, {\sl Second-Order Convex Splitting Schemes for Non-local Cahn-Hilliard and Allen-Cahn Equations}, J.~Comput.~Phys.~277 (2014) 48-71.
	\\ 
\url{https://doi.org/10.1016/j.jcp.2014.08.001}

	\item
Z.~Guan, C.~Wang, and \textbf{S.M.~Wise}, {\sl A Convergent Convex Splitting Scheme for the Periodic Nonlocal Cahn-Hilliard Equation}, Numer.~Math.~128 (2014) 377-406.
	\\ 
\url{https://doi.org/10.1007/s00211-014-0608-2}

	\item
A.~Diegel, X.~Feng, and \textbf{S.M.~Wise}, {\sl Analysis of a Mixed Finite Element Method for a Cahn-Hilliard-Darcy-Stokes System}, SIAM J.~Numer.~Anal.~53 (2015) 127-152.
	\\ 
\url{https://doi.org/10.1137/130950628}

	\item
A.~Aristotelous, O.~Karakashian, and \textbf{S.M.~Wise}, {\sl Second-Order in Time, Primitive-Variable Discontinuous Galerkin Schemes for a Cahn-Hilliard Equation with a Mass Source Term}, IMA J.~Numer.~Anal.~35 (2015) 1167-1198.
	\\ 
\url{https://doi.org/10.1093/imanum/dru035} 

	\item    
W.~Feng, T.~Lewis, and \textbf{S.M.~Wise}, {\sl Discontinuous Galerkin Derivative Operators with Applications to Second Order Elliptic Problems and Stability}, Math.~Methods~Appl.~Sci.~38 (2015) 5160-5182.
	\\ 
\url{https://doi.org/10.1002/mma.3440}  

	\item
J.~Guo, C.~Wang, \textbf{S.M.~Wise}, and X.~Yue, {\sl An $H^2$ Convergence of a Second-Order Convex-Splitting, Finite Difference Scheme for the Three-Dimensional Cahn-Hilliard Equation}, Commun.~Math.~Sci.~14 (2016) 489-515.
	\\ 
\url{https://doi.org/10.4310/CMS.2016.v14.n2.a8}

	\item
Tri Sri Noor Asih, Suzanne Lenhart, \textbf{S.M.~Wise}, Lina Aryati, F. Adi-Kusumo, Mardiah S.~Hardianti, and Jonathan Forde, {\sl The Dynamics of HPV Infection and Cervical Cancer Cells}, Bull.~Math.~Biol.~78 (2016) 4-20.
	\\ 
\url{https://doi.org/10.1007/s11538-015-0124-2}

	\item
W.~Chen, Y.~Liu, C.~Wang, and \textbf{S.M.~Wise}, {\sl An Optimal-Rate Convergence Analysis of a Fully Discrete Finite Difference Scheme for the Cahn-Hilliard-Hele-Shaw Equation}, Math.~Comp.~85 (2016) 2231-2257.
	\\ 
\url{https://doi.org/10.1090/mcom3052}

	\item
N.~Chen, C.~Wang, and \textbf{S.M.~Wise}, {\sl Global-in-time Gevrey Regularity Solution for a Class of Bistable Gradient Flows}, Discrete Cont. Dyn. Syst. Ser. B 21 (2016) 1689-1711.
	\\ 
\url{https://doi.org/10.3934/dcdsb.2016018}

	\item
Z.~Guan, V.~Heinonen, J.S.~Lowengrub, C.~Wang, and \textbf{S.M.~Wise}, {\sl An Energy Stable, Hexagonal Finite Difference Scheme for the 2D Phase Field Crystal Amplitude Equations}, J.~Comput.~Phys.~321 (2016) 1026-1054.
	\\ 
\url{https://doi.org/10.1016/j.jcp.2016.06.007}

	\item
A.~Diegel, C.~Wang, and \textbf{S.M.~Wise}, {\sl Stability and Convergence of a Second Order Mixed Finite Element Method for the Cahn-Hilliard Equation}, IMA J.~Numer.~Anal.~36 (2016) 1867-1897.
	\\ 
\url{https://doi.org/10.1093/imanum/drv065}

	\item
K.~Cheng, C.~Wang, \textbf{S.M.~Wise}, and Y.~Yue, {\sl A Second-Order, Weakly Energy-Stable Pseudo-Spectral Scheme for the Cahn-Hilliard Equation and its Solution by the Homogeneous Linear Iteration Method}, J.~Sci.~Comput.~69 (2016) 1083-1114.
	\\ 
\url{https://doi.org/10.1007/s10915-016-0228-3}

	\item
W.~Feng, A.J.~Salgado, C.~Wang, \textbf{S.M.~Wise}, {\sl Preconditioned Steepest Descent Methods for some Nonlinear Elliptic Equations Involving p-Laplacian Terms}, J.~Comput.~Phys.~334 (2017) 45-67.
	\\ 
\url{https://doi.org/10.1016/j.jcp.2016.12.046}

	\item
Y.~Liu, W.~Chen, C.~Wang, and \textbf{S.M.~Wise}, {\sl Error Analysis of a Mixed Finite Element Method for a Cahn-Hilliard-Hele-Shaw System}, Numer.~Math.~135 (2017) 679-709.
	\\ 
\url{https://doi.org/10.1007/s00211-016-0813-2}

	\item
Z.~Qiao, C.~Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl Error Analysis of an Energy Stable Finite Difference Scheme for the Epitaxial Thin Film Model with Slope Selection with an Improved Convergence Constant}, Int.~J.~Numer.~Anal.~Model.~14 (2017) 283-305.

	\item
Z.~Guo, P.~Lin, J.S.~Lowengrub, and \textbf{S.M.~Wise}, {\sl Mass Conservative and Energy Stable Finite Difference Methods for the Quasi-Incompressible Navier-Stokes-Cahn-Hilliard System: Primitive Variable and Projection-Type Schemes}, Comput.~Methods~Appl.~Mech.~Engrg.~326 (2017) 144-174.
	\\ 
\url{https://doi.org/10.1016/j.cma.2017.08.011}

	\item
A.~Diegel, C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl Error Analysis of a Second Order Mixed Finite Element Method for the Cahn-Hilliard-Navier-Stokes Equation}, Numer.~Math.~137 (2017) 495-534.
	\\ 
\url{https://doi.org/10.1007/s00211-017-0887-5}

	\item
W.~Feng, Z.~Guo, J.S.~Lowengrub, and \textbf{S.M.~Wise}, {\sl A Mass-Conservative Adaptive FAS Multigrid Solver for Cell-Centered Finite Difference Methods on Block-Structured, Locally-Cartesian Grids}, J.~Comput.~Phys.~352 (2018) 463-497.
	\\ 
\url{https://doi.org/10.1016/j.jcp.2017.09.065}

	\item
Y.~Yan, W.~Chen, C.~Wang, and \textbf{S.M.~Wise}, {\sl A Second-Order Energy Stable BDF Numerical Scheme for the Cahn-Hilliard Equation}, Commun.~Comput.~Phys.~23 (2018) 572-602.
	\\ 
\url{https://doi.org/10.4208/cicp.OA-2016-0197}


	\item
L.~Dong, W.~Feng, C.~Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl Convergence Analysis and Numerical Implementation of a Second Order Numerical Scheme for the Three-Dimensional Phase Field Crystal Equation}, Comput.~Math.~Appl.~75 (2018) 1912-1928.
	\\ 
\url{https://doi.org/10.1016/j.camwa.2017.07.012}

	\item
J.~Cummings, J.S.~Lowengrub, B.G.~Sumpter, \textbf{S.M.~Wise} and R.~Kumar, {\sl Modeling Solvent Evaporation During Thin Film Formation in Phase Separating Polymer Mixtures}, Soft Matter 14 (2018) 1833-1846.
	\\ 
\url{https://doi.org/10.1039/c7sm02560b}

	\item
L.G.~Rebholz, \textbf{S.M.~Wise}, and M.~Xiao, {\it Penalty-Projection Schemes for the Cahn-Hilliard Navier-Stokes Diffuse Interface Model of Two Phase Flow, and their Connection to Divergence-Free Coupled Schemes}, Int.~J.~Numer.~Anal.~Model.~15 (2018) 649-676.

	\item
Y.~Chen, J.S.~Lowengrub, J.~Shen, C.~Wang, and \textbf{S.M.~Wise}, {\sl Efficient Energy Stable Schemes for Isotropic and Strongly Anisotropic Cahn-Hilliard Systems with the Willmore Regularization}, J.~Comput.~Phys.~365 (2018) 56-73.
	\\
\url{https://doi.org/10.1016/j.jcp.2018.03.024}

	\item
W.~Feng, Z.~Guan, J.S.~Lowengrub, C.~Wang, \textbf{S.M.~Wise}, and Y. Chen, {\sl An Energy Stable Finite-Difference Scheme for the Functionalized Cahn-Hilliard Equation and its Convergence Analysis}, J.~Sci.~Comput.~76 (2018) 1938-1967.
	\\ 
\url{https://doi.org/10.1007/s10915-018-0690-1}

	\item
W.~Feng, C.~Wang, \textbf{S.M.~Wise},  Z.~Zhang, {\sl A Second-Order Energy Stable Backward Differentiation Formula Method for the Epitaxial Thin Film Equation with Slope Selection}, Numer.~Methods~Partial~Differ.~Eq.~34 (2018) 1975-2007.
	\\ 
\url{https://doi.org/10.1002/num.22271}

	\item
R.~Backofen, \textbf{S.M.~Wise}, M.~Salvalaglio, and A.~Voigt, {\sl Convexity Splitting in a Phase Field Model for Surface Diffusion}, Int.~J.~Numer.~Anal.~Model.~16 (2019) 192-209.

	\item
W.~Chen, W.~Feng, Y.~Liu, C.~Wang, and \textbf{S.M.~Wise}, {\sl A Second Order Energy Stable Scheme for the Cahn-Hilliard-Hele-Shaw Equations}, Discrete Cont.~Dyn.~Syst.~Ser.~B 24 (2019) 149-182.
	\\ 
\url{https://doi.org/10.3934/dcdsb.2018090}

		\item
K.~Cheng, W.~Feng, C.~Wang, and \textbf{S.M.~Wise}, {\sl An Energy Stable Fourth Order Finite Difference Scheme for the Cahn-Hilliard Equation}, J.~Comput.~Appl.~Math.~362 (2019) 574-595.
	\\ 
\url{https://doi.org/10.1016/j.cam.2018.05.039}

    \item
W.~Chen, C.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl Positivity-Preserving, Energy Stable Numerical Schemes for the Cahn-Hilliard Equation with Logarithmic Potential}, J.~Comput.~Phys.~X 3 (2019) 100031 (29 pages).
	\\ 
\url{https://doi.org/10.1016/j.jcpx.2019.100031}

	\item
J.M.~Church, Z.~Guo, P.K.~Jimack, A.~Madzvamuse, K.~Promislow, B.~Wetton, \textbf{S.M.~Wise}, and F.~Yang, {High Accuracy Benchmark Problems for Allen-Cahn and Cahn-Hilliard Dynamics},  Commun.~Comput.~Phys.~26 (2019), pp. 947-972.
	\\ 
\url{https://doi.org/10.4208/cicp.OA-2019-0006}

	\item
K.~Cheng, C.~Wang, and \textbf{S.M.~Wise}, {\sl An Energy Stable BDF2 Fourier Pseudo-Spectral Numerical Scheme for the Square Phase Field Crystal Equation}, Commun.~Comput.~Phys.~26 (2019) 1335-1364.
	\\ 
\url{https://doi.org/10.4208/cicp.2019.js60.10}

	\item
K.~Cheng, C.~Wang, \textbf{S.M.~Wise}, and Z. Yuan, {\sl Global-in-Time Gevrey Regularity Solutions for the Functionalized Cahn-Hilliard Equation}, Discrete Cont.~Dyn.~Syst.~Ser.~S 13 (2020) 2211-2229.
	\\ 
\url{https://doi.org/10.3934/dcdss.2020186}

	\item
K.~Cheng, C.~Wang, and \textbf{S.M.~Wise}, {\sl A Weakly Nonlinear, Energy Stable Scheme for the Strongly Anisotropic Cahn-Hilliard Equation and Its Convergence Analysis}, J.~Comput.~Phys.~405 (2020) 109109 (28 pages).
	\\ 
\url{https://doi.org/10.1016/j.jcp.2019.109109}

	\item
L.~Chen, X.~Hu, and \textbf{S.M.~Wise}, {\sl Convergence Analysis of the Fast Subspace Descent Methods for Convex Optimization Problems}, Math.~Comp.~89, (2020) 2249-2282.
	\\ 
\url{https://doi.org/10.1090/mcom/3526}

	\item
W.~Chen, C.~Wang, S.~Wang, X.~Wang, and \textbf{S.M.~Wise}, {\sl Energy Stable Numerical Schemes for a Ternary Cahn-Hilliard System}, J.~Sci.~Comp.~84 (2020) 27 (36 pages).
	\\ 
\url{https://doi.org/10.1007/s10915-020-01276-z}

	\item
C.~Zhang, J.~Ouyang, C.~Wang, and \textbf{S.M.~Wise}, {\sl Numerical Comparison of Modified-Energy Stable SAV-Type Schemes and Classical BDF Methods on Benchmark Problems for the Functionalized Cahn-Hilliard Equation}, J.~Comput.~Phys.~423 (2020) 109772 (35 pages).
	\\ 
\url{https://doi.org/10.1016/j.jcp.2020.109772}

	\item
Z.~Guo, F.~Yu,  P.~Lin, \textbf{S.M.~Wise}, and J.S.~Lowengrub, {\sl A Diffuse Domain Method for Two Phase Flows with Large Density Ratio in Complex Geometries}, J.~Fluid Mech.~907 (2021) A38.
	\\
\url{https://doi.org/10.1017/jfm.2020.790}

	\item
J.~Guo, C.~Wang, \textbf{S.M.~Wise} and X. Yue, {\sl An Improved Error Analysis for a Second-Order Numerical Scheme for the Cahn-Hilliard Equation}, J.~Comput.~Appl.~Math.~388 (2021). 113300.
	\\
\url{https://doi.org/10.1016/j.cam.2020.113300}

	\item
M. Salvalaglio, A. Voigt, and \textbf{S.M.~Wise}, {\sl Doubly Degenerate Diffuse Interface Models of Surface Diffusion}, Math.~Methods Appl.~Sci.~44 (2021) 5385--5405.
	\\
\url{https://doi.org/10.1002/mma.7116}

	\item
M. Salvalaglio, M. Selch, A. Voigt, and \textbf{S.M.~Wise}, {\sl Doubly Degenerate Diffuse Interface Models of Anisotropic Surface Diffusion}, Math.~Methods Appl.~Sci.~44 (2021) 5406--5417.
	\\
\url{https://doi.org/10.1002/mma.7118}

	\item
M.~Yuan, W.~Chen, C. Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl An Energy Stable Finite Element Scheme for the Three-Component Cahn-Hilliard-Type Model for Macromolecular Microsphere Composite Hydrogels}, J.~Sci.~Comp.~87 (2021) 78.
	\\ 
\url{https://doi.org/10.1007/s10915-021-01508-w}

	\item
J.~Zhang, C.~Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl Structure-preserving, Energy Stable Numerical Schemes for a Liquid Thin Film Coarsening Model}, SIAM J.~Sci.~Comput.~42 (2021) A1248--A1272.
	\\ 
\url{https://doi.org/10.1137/20M1375656}

	\item
L.~Dong, C.~Wang, \textbf{S.M.~Wise}, and Z. Zhang, {\sl A Positivity-Preserving, Energy Stable Scheme for a Ternary Cahn-Hilliard System with Singular Interfacial Parameters}, J.~Comput.~Phys.~442 (2021) 110451 (29 pages).
	\\ 
\url{https://doi.org/10.1016/j.jcp.2021.110451}

	\item
C.~Liu, C.~Wang, \textbf{S.M.~Wise}, X.~Yue, and S.~Zhou, {\sl A Positivity-Preserving, Energy Stable and Convergent Numerical Scheme for the Poisson-Nernst-Planck System}, Math.~Comp.~90 (2021) 2071--2106.
	\\ 
\url{https://doi.org/10.1090/mcom/3642}

	\item
S.~Sahyoun, D.~Wilson, S.M.~Djouadi, \textbf{S.M.~Wise}, H.A.~Abderrahmane, {\sl Proper Orthogonal Decomposition Reduced Order Model for Tear Film Flows}, American Control Conference (ACC) (2021) 2763--2768.
	\\
\url{https://doi.org/10.23919/ACC50511.2021.9483018}

	\item
J.~Park, A.J.~Salgado, and \textbf{S.M.~Wise}, {\sl Preconditioned Accelerated Gradient Descent Methods for Locally Lipschitz Smooth Objectives with Applications to the Solution of Nonlinear PDEs}, J.~Sci.~Comput.~89 (2021) 17 (37 pages).
	\\ 
\url{https://doi.org/10.1007/s10915-021-01615-8}

	\item
W.~Chen, J.~Jing, C.~Wang, X.~Wang and \textbf{S.M.~Wise}, {\sl A Modified Crank-Nicolson Numerical Scheme for the Flory-Huggins Cahn-Hilliard Model}, Commun.~Comput.~Phys.~31 (2022), 60--93.
	\\ 
\url{https://doi.org/10.4208/cicp.OA-2021-0074}

	\item
C.~Liu, C.~Wang, \textbf{S.M.~Wise}, X.~Yue, and S.~Zhou, {\sl An Iterative Solver for the Poisson-Nernst-Planck System and its Convergence Analysis},  J.~Comput.~Appl.~Math.~406 (2022) 114017 (13 pages).
	\\ 
\url{https://doi.org/10.1016/j.cam.2021.114017}

	\item
C.~Liu, C.~Wang, Y.~Wang, and \textbf{S.M.~Wise}, {\sl Convergence Analysis of the Variational Operator Splitting Scheme for a Reaction-Diffusion System with Detailed Balance}, SIAM J.~Numer.~Anal.~60 (2022) 781--803.
	\\
\url{https://doi.org/10.1137/21M1421283}

	\item
K.~Cheng, C.~Wang, \textbf{S.M.~Wise}, and Y.~Wu, {\sl A Third Order Accurate in Time, BDF-Type Energy Stable Scheme for the Cahn-Hilliard Equation}, Numer.~Math.~Theor.~Meth.~Appl.~15 (2022) 279--303.
	\\
\url{https://doi.org/10.4208/nmtma.OA-2021-0165}

	\item
L.~Dong, C.~Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl Optimal Rate Convergence Analysis of a Numerical Scheme for the Ternary Cahn-Hilliard System with a Flory-Huggins-deGennes Energy Potential}, J.~Comp.~Appl.~Math.~415 (2022) 114474 (18 pages).
	\\
\url{https://doi.org/10.1016/j.cam.2022.114474}

	\item
E.~Habbershaw and \textbf{S.M.~Wise}, {\sl A Progress Report on Numerical Methods for BGK-Type Kinetic Equations}, TRACE: Faculty Publications and Other Works, Mathematics, The University of Tennessee (2022) Report number 10.
 	\\
\url{https://trace.tennessee.edu/utk_mathpubs/10/}

	\item
M.~Yuan, W.~Chen, C.~Wang, \textbf{S.M.~Wise}, and Z.~Zhang, {\sl A Second Order Accurate in Time, Energy Stable Finite Element Scheme for the Flory-Huggins-Cahn-Hilliard Equation}, 14 (2022) 1477--1508.

\url{https://doi.org/10.4208/aamm.OA-2021-0331}

	\item
M.~Punke, \textbf{S.M.~Wise}, A.~Voigt, and M.~Salvalaglio, {\sl  Explicit Temperature Coupling in Phase-Field Crystal Models of Solidification}, Modelling~Simul.~Mater.~Sci.~Eng.~30 (2022) 074004 (18 pages).
	\\ 
\url{https://doi.org/10.1088/1361-651X/ac8abd}

	\item
C.~Wang  and \textbf{S.M.~Wise}, {\sl A Thermodynamically-Consistent Phase Field Crystal Model of Solidification with Heat Flux}, J.~Math.~Study~55 (2022) 1--21.
	\\
\url{https://doi.org/10.4208/jms.v55n4.22.01}

	\item
X.~Chen, C.~Wang, and \textbf{S.M.~Wise}, {\sl A Preconditioned Steepest Descent Solver for the Cahn-Hilliard Equation with Variable Mobility}, Int.~J.~Numer.~Anal.~Model.~19 (2022) 839--863.
	\\
\url{http://www.math.ualberta.ca/ijnam/Volume-19-2022/No-6-22/2022-06-06.pdf}

	\item
J.H.~Park, A.J.~Salgado, and \textbf{S.M.~Wise}, {\sl Benchmark Computations of the Phase Field Crystal and Functionalized Cahn-Hilliard Equations via Fully Implicit, Nesterov Accelerated Schemes}, Commun.~Comput.~Phys.~(in press).

	\item
K.~Cheng, C.~Wang, and \textbf{S.M.~Wise}, {\sl An Energy Stable Finite Difference Scheme for the Ericksen-Leslie System with Penalty Function and its Optimal Rate Convergence Analysis}, Commun.~Math.~Sci.~(in review).
	\\ 
Preprint at \url{www.math.utk.edu/~swise/Site/Publications.html}

	\item
A.~Christlieb, K.~Promislow, Z.~Tan, S.~Wang, B.~Wetton, \textbf{S.M.~Wise}, {\sl Benchmark Computation of Morphological Complexity in the Functionalized Cahn-Hilliard Gradient Flow}, Commun.~Comput.~Phys.~(in review).
	\\ 
Preprint at \url{https://arxiv.org/abs/2006.04784}

	\item
K.~Cheng, C.~Wang, and \textbf{S.M.~Wise}, {\sl High Order Accurate and Convergent Numerical Scheme for the Strongly Anisotropic Cahn-Hilliard Model}, Numer. Methods Partial Diff.~Eq.~(in review).
	\\ 
Preprint at \url{www.math.utk.edu/~swise/Site/Publications.html}

	\item
C.~Wang, J.~Wang, \textbf{S.M.~Wise}, Z.~Xia, and L.~Xu, {\sl Convergence Analysis of a Temporally Second-Order Accurate Finite Element scheme for the Cahn-Hilliard-Magnetohydrodynamics System of Equations}, (in review).
	\\ 
Preprint at \url{www.math.utk.edu/~swise/Site/Publications.html}

	\item
C.~Liu, C.~Wang, \textbf{S.M.~Wise}, X.~Yue, and S.~Zhou, {\sl A Second Order Accurate Numerical Method for the Poisson-Nernst-Planck System in the Energetic Variational Formulation}, IMA J.~Numer.~Anal.~(in review).
	\\
Preprint at \url{https://arxiv.org/abs/2208.06123}

	\item
X.~Tang, S.~Li, J.S.~Lowengrub, and \textbf{S.M. Wise}, {\sl Phase Field Modeling and Computation of Vesicle Growth or Shrinkage}, J.~Math.~Biol.~(in review).
	\\
Preprint at \url{https://arxiv.org/abs/2209.13690}

	\item
M.~Punke, \textbf{S.M. Wise}, A.~Voigt, and M.~Salvalaglio, {\sl Improved Time Integration for Phase-Field Crystal Models of Solidification}, Proc.~Appl.~Math.~Mech.~(in press).
	\\
Preprint at \url{https://arxiv.org/abs/2210.04329}

	\item
Shibin Dai, Joseph Renzi, and \textbf{Steven M. Wise}, {\sl Gamma Convergence of the DeGennes-Cahn-Hilliard Energy}, Comm.~Math.~Sci.~(in press). 
	\\
Preprint at \url{https://arxiv.org}

	\end{enumerate}



{\LARGE\bf Invited Research Presentations}
%    \begin{description}
%    \item
%\textbf{Contributed}
%	\begin{enumerate}
%    \item
%Third SIAM Conference on Mathematical Aspects of Materials Science, Philadelphia, PA (May 2000). Research poster.
%    \item
%Frontiers of Nanostructured Systems, Charlottesville, VA (October 2001). Research poster.
%    \item
%TMS Fall Meeting, Indianapolis, IN (November 2001). Research talk entitled {\sl Competitive Phase Growth in Stressed Binary Systems}.
%    \item
%Differential Equations and Dynamical Systems Seminar, Mathematics Department, University of Virginia (October 2002).  Research talk entitled {\sl Coupled Conserved and Non-conserved Gradient Flow Equations for Phase Transformations}.
%    \item
%MRS Fall Meeting, Boston, MA (November 2004).  Research talk entitled {\sl Efficient Phase-Field Simulation of Faceted Quantum Dot Formation in a Strained Heteroepitaxial Film.}
%    \item
%Barrett Lectures, Mathematics Department, University of Tennessee (April 2007).  Research poster entitled {\sl The Strongly Anisotropic Cahn-Hilliard Equation.}
%	\item
%University of Tennessee and Oak Ridge National Laboratory, Computational Fluid Dynamics Working Group, Knoxville, TN (October 2007).  Seminar talk entitled {\sl A Diffuse Interface Fluid Model of Tumor Growth}.
%    \item
%University of Tennessee, Mathematics Department, Knoxville, TN (April 2009).  Seminar talk entitled {\sl Energy Stable and Convergent Schemes for the Phase Field Crystal (PFC) and Modified Phase Field Crystal (MPFC) Equations}.
%	\item
%SIAM Conference on Mathematical Aspects of Materials Science, Philadelphia, PA (May 2010). Research talk entitled {\sl Energy Stable Schemes for the Phase Field Crystal Equation}.
%	\item
%Southeastern-Atlantic Regional Conference on Differential Equations, Virginia, Tech, Blacksburg, VA (October 2010). Research talk entitled {\sl Stable Finite Difference, Adaptive Nonlinear Multigrid Simulation of a Diffuse-Interface Model For Tumor Growth}.
%	\item
%ICIAM, Vancouver, BC, Canada (July 2011). Research entitled {\sl Some Numerical Methods for  PFC and PFC-like Equations}.
%	\end{enumerate}
%	\item
%\textbf{Invited}
    \begin{enumerate}
    \item
Fourth SIAM Conference on Mathematical Aspects of Materials Science, Los Angeles, CA (May 2004). Research talk entitled {\sl Phase Field Simulation of Quantum Dot Formation in a Thin Film}.
    \item
University of Virginia MRSEC/Lund University meeting, Lund, Sweden (July 2004). Research talk entitled {\sl Phase Field Simulation of Quantum Dot Formation in a Thin Film}.
    \item
TMS Annual Meeting, The Armen G. Khachaturyan Symposium on Phase Transformation and Microstructural Evolution in Crystalline Solids, San Francisco, CA (February 2005).  Research talk entitled {\sl 3D Phase Field Simulation of Q-Dot Formation (in a Strained Heteroepitaxial Film)}.
    \item
University of Buffalo, Mathematics Department, Buffalo, NY (January 2006).  Colloquium talk entitled {\sl Diffuse-Interface/Adaptive-Multigrid Calculations of Crystal Growth with Strong Interfacial Anisotropy}.
    \item
Research Center Caesar, Crystal Growth Group, Bonn, Germany (August 2006).  Seminar talk entitled {\sl Diffuse-Interface/Adaptive-Multigrid Calculations of Crystal Growth with Strong Interfacial Anisotropy}.
    \item
SIAM Conference on Nonlinear Waves and Coherent Structures (NW06), Seattle WA (September 2006).  Research talk entitled {\sl Continuum Models of Tumor Growth and Angiogenesis}.
    \item
University of Akron, Department of Theoretical and Applied Mathematics, Akron, OH (December 2006).  Colloquium talk entitled {\sl Modeling Solid Tumor Growth: Role of the Microstructure}.
    \item
Purdue University, Mathematics Department, West Lafayette, IN (January 2007).  Colloquium talk entitled {\sl Modeling Solid Tumor Growth: Role of the Microstructure}.
    \item
University of Louisville, Mathematics Department, Louisville, KY (January 2007).  Colloquium talk entitled {\sl Modeling Solid Tumor Growth: Role of the Microstructure}.
    \item
Ohio State University, Mathematics Department and Mathematical Biosciences Institute, Columbus, OH (February 2007).  Colloquium talk entitled {\sl Modeling Solid Tumor Growth: Role of the Microstructure}.
    \item
University of Tennessee, Mathematics Department, Knoxville, TN (February 2007).  Colloquium talk entitled {\sl Modeling Solid Tumor Growth: Role of the Microstructure}.
    \item
British Applied Mathematics Colloquium, Bristol, UK (April 2007).  Research talk entitled {\sl Computational Results for a Class of Regularized, Strongly Anisotropic Cahn-Hilliard Equations}.
    \item
Florida State University, Mathematics Department, Tallahassee, FL (September 2007).  Colloquium talk entitled {\sl The Diffuse Interface Method: Applications in Tumor Growth and Phase Transformations}.
	\item
SIAM Conference on Mathematical Aspects of Materials Science, Philadelphia, PA (May 2008). Research talk entitled {\sl Large-Scale Coarsening Dynamics of Four-Fold Anisotropic Thin Films}.
    \item
Pennsylvania State University, Mathematics Department, University Park, PA (March 2009).  Seminar talk entitled {\sl Energy Stable and Convergent Schemes for the Phase Field Crystal (PFC) and Modified Phase Field Crystal (MPFC) Equations}.
	\item
33rd SIAM Southeastern-Atlantic Section Conference, University of South Carolina, Columbia, SC (April 2009).  Research talk entitled {\sl Energy Stable and Convergent Schemes for the Phase Field Crystal (PFC) and Modified Phase Field Crystal (MPFC) Equations}.
	\item
24th Annual Shanks Lecture and Conference, Vanderbilt University, Nashville, TN (May 2009). Plenary talk entitled {\sl Multiscale Modeling of Solid Tumor Growth and Angiogenesis: The Effect of the Microenvironment}.
	\item
SIAM Conference on Mathematics for Industry: Challenges and Frontiers, San Francisco, CA (October 2009). Research talk entitled {\sl Energy Stable and Convergent Schemes for the Phase Field Crystal (PFC) and Modified Phase Field Crystal (MPFC) Equations}.
    \item
University of Massachusetts, Mathematics Department, North Dartmouth, MA (November 2009).  Seminar talk entitled {\sl Energy Stable and Convergent Schemes for Bistable Gradient Equations}.
    \item
University of Pittsburgh, Mathematics Department, Pittsburgh, PA (January 2010).  Colloquium talk entitled {\sl Convex Splitting Schemes for Conserved Bistable Gradient Equations: Applications in Grain Boundary Motion, Solidification, and Tumor Growth}.
    \item
Purdue University, Mathematics Department, West Lafayette, IN (March 2010).  Seminar talk entitled {\sl Convex Splitting Schemes for Conserved Bistable Gradient Equations: Applications in Grain Boundary Motion, Solidification, and Tumor Growth}.
	\item
AMS Southeastern Section Meeting, University of Kentucky, Lexington, KY (March 2010). Research talk entitled {\sl Energy Stable and Convergent Schemes for the Phase Field Crystal (PFC) and Modified Phase Field Crystal (MPFC) Equations}.
	\item
SIAM Annual Meeting, Pittsburgh, PA (July 2010). Research talk entitled {\sl An Unconditionally Stable Second-Order Scheme for the Slope Selection Equation and Related Epitaxial Thin Film Models}.
	\item
SIAM Conference on the Life Sciences, Pittsburgh, PA (July 2010). Research talk entitled {\sl Stable Finite Difference, Adaptive Nonlinear Multigrid Simulation of a Diffuse-Interface Model for Tumor Growth}.
	\item
University of South Carolina, Columbia SC (October 2010). Seminar talk entitled {\sl Numerical and PDE Analyses of a Diffuse-Interface Model for Tumor Growth}.
	\item
Central Michigan University, Mount Pleasant, MI (March 2011). Seminar talk entitled {\sl Numerical and PDE Analyses of a Diffuse-Interface Model for Tumor Growth}.
	\item
35th SIAM Southeastern-Atlantic Section Conference, University of North Carolina, Charlotte, NC (March 2011).  Research talk entitled {\sl Second-Order Convex-Splitting Schemes}.
	\item
SIAM Conference on Applications of Dynamical Systems, Snowbird, UT (May 2010). (Declined invitation.)
	\item
2011 International Conference on Applied Mathematics and Interdisciplinary Research, Nankai University, Tianjin, China and Beijing, China (June 2011). (Declined invitation.)
	\item
ICIAM, Vancouver, BC, Canada (July 2011). Research talk entitled {\sl Second-Order Convex-Splitting Schemes}. (Declined invitation because of a scheduling conflict.)
	\item
University of South Carolina, Columbia, SC (January 2012). Research talk entitled {\sl PDE/Numer-ical Analyses and Computations of some Diffuse Interface Models of Viscous Two-Phase Flows}.
	\item
Florida State University, Tallahassee, FL (February 2012). Research talk entitled {\sl PDE/Numerical Analyses and Computations of some Diffuse Interface Models of Viscous Two-Phase Flows}.
	\item
Illinois Institute of Technology, Chicago, IL (March 2012). Research talk entitled {\sl PDE/Numer-ical Analyses and Computations of some Diffuse Interface Models of Viscous Two-Phase Flows}.
	\item
ORNL/UTK Numerical Day 2012, Oak Ridge National Lab, Oak Ridge, TN (April 2012). Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for the Cahn-Hilliard Equation}.
	\item
University of California, Irvine, CA (May 2012). Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for a Modified Cahn-Hilliard Equation}.
	\item
Workshop on {\sl Heterostructured Nanocrystalline Materials}, ICERM, Brown University, Providence, RI (May 2012). (Declined invitation because of a scheduling conflict.)
	\item
AIMS 9th International Conference On Dynamical Systems and Differential Equations, Orlando, FL (July 2012). Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for the Cahn-Hilliard Equation}.
	\item
George Mason University, Fairfax, VA (September 2012). Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for the Cahn-Hilliard Equation}.
	\item
Virginia Tech, Blacksburg, VA (September 2012). Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for the Cahn-Hilliard Equation}.
	\item
{\sl Workshop II: Atomistic and Mesoscale Modeling of Materials Defects}, IPAM's Program on {\sl Materials Defects: Mathematics, Computation, and Engineering}, University of California, Los Angeles, CA (October 2012). Research talk entitled {\sl Some Numerical Methods for PFC and DDFT-Like Equations}.
	\item
{\sl International Workshop on Acoustic Activation of Surface Processes},  Breckenridge, CO (January 2013).  Sponsored by DARPA. (Unable to attend due to a late scheduling conflict.)
	\item
SIAM Conference on Computational Science and Engineering, Boston, MA (February 2013).  Research talk entitled {\sl A Mixed Discontinuous Galerkin, Convex Splitting Scheme for the Cahn-Hilliard Equation}.
	\item
37th SIAM Southeastern-Atlantic Section Conference, University of Tennessee, Knoxville, TN (March 2013).  Research talk entitled {\sl Second-Order Convex-Splitting Linear Iteration Scheme for Thin Film Models}.
	\item
University of Virginia, Charlottesville, VA (June 2013).  Research talk entitled {\sl The Phase Field Crystal Model: A Continuum Framework for Studying Phase Transformations on Atomic Length and Diffusive Time Scales}.
	\item
Oak Ridge National Lab, Computational Mathematics Seminar, Oak Ridge, TN (March 2014). Research talk entitled {\sl Convergence of a Mixed Finite Element Method for a Cahn-Hilliard-Stokes System}.
	\item
University of North Carolina, Greensboro, NC (March 2014). Research talk entitled {\sl Convergence of a Mixed Finite Element Method for a Cahn-Hilliard-Stokes System}.
	\item
Soochow University, Suzhou, China (June 2014). Research talk entitled {\sl Convergence of a Mixed Finite Element Method for a Cahn-Hilliard-Stokes System}.
	\item
Fudan University, Shanghai, China (June 2014). Research talk entitled {\sl Convergence of a Mixed Finite Element Method for Some Cahn-Hilliard-Flow Models}.
	\item
Shanghai Jiao Tong University, Shanghai, China (June 2014). Research talk entitled {\sl Convergence of a Mixed Finite Element Method for Some Cahn-Hilliard-Flow Models}.
	\item
SIAM Annual Meeting, Chicago, IL (July 2014). Research talk entitled {\sl Optimal Energy Norm Error Estimates for a Mixed FEM for a Cahn-Hilliard-Stokes System}.
	\item
SIAM Annual Meeting, Chicago, IL (July 2014). Research talk entitled {\sl Stable and Convergent Numerical Schemes for Phase Field Crystal Models}.
	\item
Virginia Tech, Blacksburg, VA (October 2014).  Research talk entitled {\sl The Phase Field Crystal Model: A Continuum Framework for Studying Phase Transformations on Atomic Length and Diffusive Time Scales}.
	\item
Penn State, State College, PA (October 2014).  Research talk entitled {\sl The Phase Field Crystal Model: A Continuum Framework for Studying Phase Transformations on Atomic Length and Diffusive Time Scales}.
	\item
AMS Southeastern Section Meeting, Memphis, TN (October 2015). Research talk entitled {\sl Convergence of a Second-order-in-time Finite Element Scheme for the Cahn-Hilliard Equation}.
	\item
SIAM SEAS 2016, Athens, GA (March 2016). Research talk entitled {\sl Stability and Convergence for some Numerical Approximations of Cahn-Hilliard-Navier-Stokes Systems}.
	\item
Florida State University, Tallahassee, FL (March 2016). Research talk entitled {\sl A Convergent, Energy Stable, and Efficient Hexagonal Finite Difference Scheme for the Phase Field Crystal Amplitude Expansion Model}.
	\item
Michigan State University, East Lansing, MI (April 2016). Research talk entitled {\sl Higher-Order Convex Splitting Schemes for Bi-Stable Gradient Equations: Analysis and Practical Implementation}.
	\item
AIMS 11th International Conference on Dynamical Systems and Differential Equations, Orlando, FL (July 2016). Research talk entitled {\sl A Convergent, Energy Stable, and Efficient Hexagonal Finite Difference Scheme for the Phase Field Crystal Amplitude Expansion Model}.
	\item
AIMS 11th International Conference on Dynamical Systems and Differential Equations, Orlando, FL (July 2016). Research talk entitled {\sl A Multiphase Thin Film Model for Polymer Organic Photovoltaic (OPV) Device Preparation}.
	\item
Penn State, State College, PA (August 2016).  Research talk entitled {\sl A Multi-Component Model for Solvent Evaporation in a Polymer Thin Film}.
	\item
Virginia Tech, Blacksburg, VA (November 2016).  Research talk entitled {\sl Preconditioned Steepest Descent Methods for some Nonlinear Elliptic Equations Involving p-Laplacian Terms}.
	\item
University of North Carolina, Chapel Hill, NC (March 2017).  Research talk entitled {\sl Diffuse Interface Models of Density Mismatched, Multi-Phase Flows and Their Approximation Using Adaptive Multigrid Methods}.
	\item
University of California, Irvine, CA (April 2017).  Research talk entitled {\sl Preconditioned Steepest Descent Methods for some Nonlinear Elliptic Equations Involving p-Laplacian Terms}.
	\item
Oak Ridge National Laboratory, Computational and Applied Mathematics Seminar, Oak Ridge, TN (June 2017).  Research talk entitled {\sl Diffuse Interface Models of Density Mismatched, Multi-Phase Flows and Their Approximation Using Adaptive Multigrid Methods}.
	\item
Technical University of Dresden, The Dresden Fellow Lecture, Mathematics Department, Dresden, Germany (November 2017).  Research talk entitled {\sl Diffuse Interface Models of Density Mismatched, Multi-Phase Complex Fluids, Soft Matter, and Beer Bubbles}.
	\item
Tufts University, Medford, MA (March 2018).  Research talk entitled {\sl Preconditioned Gradient Descent Methods for some Nonlinear Elliptic Equations Involving p-Laplacian Terms}.
	\item
SIAM Conference on Nonlinear Waves, Anaheim, CA (June 2018). Research talk entitled {\sl A Phase Field Crystal Model for Graphene and Some Benchmark Problems}.
	\item
Illinois Institute of Technology, Chicago, IL (October 2018).  Research talk entitled {\sl Convergence Analysis of a Generalized Full Approximation Storage Scheme for Convex Optimization Problems}.
	\item
University of Alabama, Tuscaloosa, AL (March 2019).  Research talk entitled {\sl Convergence Analysis of Fast Subspace Descent (FASD) Scheme for Convex Optimization Problems}.
	\item
University of California, Irvine, CA (April 2019).  Research talk entitled {\sl Convergence Analysis of Fast Subspace Descent (FASD) Scheme for Convex Optimization Problems}.
	\item
2019 Midwest Numerical Analysis Day, Illinois Institute of Technology, Chicago, IL (April 2019).  Research talk entitled {\sl A New Thermodynamically Consistent Phase Field Crystal Model with Multiple Phases and Heat Transport}.
	\item
Missouri University of Science and Technology, Rolla, MO (May 2019).  Research talk entitled {\sl Convergence Analysis of Fast Subspace Descent (FASD) Scheme for Convex Optimization Problems}.
	\item
The Cahn-Hilliard Equation: Recent Advances and Applications, NSF/CBMS Conference (May 2019). Research talk entitled {\sl Convergence Analysis of Fast Subspace Descent (FASD) Scheme for Convex Optimization Problems Especially for Cahn-Hilliard-Type Equations}.
	\item
CAIMS Annual Meeting, Whistler, BC, Canada (June 2019). Research talk entitled {\sl Numerical Methods and Benchmark Computations for the Functionalized Cahn-Hilliard Equation}. (Unable to attend due to a late flight cancellation. Talk given by a co-author.)
	\item
The University of Pittsburgh, Pittburgh, PA (September 2019).  Research talk entitled {\sl Convergence Analysis of Fast Subspace Descent (FASD) Scheme for Convex Optimization Problems}.

	\end{enumerate}

	\smallskip

{\LARGE\bf General Audience Presentations}

    \begin{enumerate}
    \item
Tennessee Governor's School, October 2010. Gave presentation entitled {\sl How to Become a Mathematician, and Maybe What to Do After That}.
    
    \item
University of Tennessee Pregame Faculty Showcase, November, 2013. Gave presentation entitled {\sl Simulations for Solutions: Solving Problems Through Scientific Computing}.
    
    \item
University of Tennessee Governor's School for the Sciences and Engineering, June, 2016. Gave presentation entitled {\sl Solving Problems with Scientific Computing, or Computing with Floating Point Numbers}.

	\item
University of Tennessee, High school teacher training event {\sl Let's Get Physical! Teaching Mathematics through the Lens of Physics}, July, 2016. Gave presentation entitled {\sl  Modeling Soft Matter Materials}.

	\end{enumerate}
	
	\smallskip
	
	{\LARGE\bf  Recent Teaching}
    \begin{description}
    \item
Math 572, Numerical Mathematics II, Spring 2023.
	\item
Math 547, Applied Linear Analysis, Spring 2023.
    
    \item
Math 571, Numerical Mathematics I, Fall 2022.
    \item
Math 171, Computer Literacy for Mathematics, Spring 2021.
    \item
Math 674, Advanced Numerical PDE II, Spring 2021.
    \item
Math 673, Advanced Numerical PDE I, Fall 2021.
    \item
Math 572, Numerical Mathematics II, Spring 2019.
    \item
Math 571, Numerical Mathematics I, Fall 2018.
    \item
Math 171, Computer Literacy for Mathematics, Spring 2018.
    \item
Math 341, Introduction to Analysis, Spring 2018.
    \item
Math 572, Numerical Mathematics II, Spring 2017.
    \item
Math 674/579, Numerical Stochastic Differential Equations II, Spring 2017.
    \item
Math 571, Numerical Mathematics I, Fall 2016.
    \item
Math 579, Numerical Stochastic Differential Equations I, Fall 2016.

%    \item
%Math 171, Computer Literacy for Mathematics.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring16/math171/}
%    \item
%Math 572, Numerical Mathematics II.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring16/math572/}
%    \item
%Math 545, Real Analysis (Measure Theory and Integration).
%\newline\url{http://www.math.utk.edu/~swise/classes/fall15/math545/}
%    \item
%Math 673, Advanced Topics in Numerical PDE I (Multigrid Convergence Analysis).
%\newline\url{http://www.math.utk.edu/~swise/classes/fall14/math673/}
	\end{description}
%    \item
%Math 448, Honors Advanced Calculus II.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring14/math448/}
%    \item
%Math 547, Applied Linear Analysis.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring14/math547/}
%    \item
%Math 447, Honors Advanced Calculus I.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall13/math447/}	
%    \item
%Math 574, Finite Element Methods.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring13/math574/}
%	\item
%Math 636, Advanced Partial Differential Equations II.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring13/math636/}
%	\item
%Math 200, Matrix Computations.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall12/math200/}
%	\item
%Math 572, Numerical Mathematics II.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring12/math572/}
%	\item
%Math 472, Numerical Algebra.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring12/math472/}
%	\item
%Math 571, Numerical Mathematics I.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall11/math571/}
%	\item
%Math 241, Calculus III.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall11/math241/}
%	\item
%Math 403, Mathematical Methods for Engineers and Scientists.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall10/math403/}
%	\item
%Math 681, Advanced Mathematical Ecology I.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall10/math681/}
%	\item
%Math 572, Numerical Mathematics II.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring10/math572/}
%	\item
%Math 571, Numerical Mathematics I.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall09/math571/}
%	\item
%Math 251, Matrix Algebra.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall09/math251/}
%	\item
%Spring Semester 2009:  Math 472, Numerical Algebra.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring09/math472/}
%	\item
%Spring Semester 2009:  Math 404, Applied Vector Calculus.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring09/math404/}
%	\item
%Fall Semester 2008:  Math 471, Numerical Analysis.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall08/math471/}
%	\item
%Spring Semester 2008:  Math 231, Differential Equations.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring08/math231/}
%	\item
%Spring Semester 2008:  Math 371, Numerical Methods.
%\newline\url{http://www.math.utk.edu/~swise/classes/spring08/math371/}
%	\item
%Fall Semester 2007:  Math 251, Matrix Algebra.
%\newline\url{http://www.math.utk.edu/~swise/classes/fall07/math251/}
%	\item
%Spring Quarter 2007:  Math 112C, Introduction to Partial Differential Equations and Applications.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/spring07/math112c/}
%	\item
%Winter Quarter 2007:  Math 112B, Introduction to Partial Differential Equations and Applications.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/winter07/math112b/}
%	\item
%Fall Quarter 2006:  Math 121A, Linear Algebra.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/fall06/math121a/}
%	\item
%Spring Quarter 2006:  Math 121A, Linear Algebra.
%	\item
%Fall Quarter 2005:  Math 112A, Introduction to Partial Differential Equations and Applications.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/fall05/math112a/}
%	\item
%Spring Quarter 2005:  Math 146, Fourier Analysis.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/spring05/math146}
%	\item
%Spring Quarter 2003:  Math 2B, Calculus II.
%	\newline
%\url{http://www.math.utk.edu/~swise/classes/spring03/math2b/}


%	\smallskip
%
%{\LARGE\bf Software}
%	
%Block-Structured Adaptive Multigrid (BSAM). Current version: 1.2. Version in development: 2.0.
%
%\url{https://github.com/bsam} \quad -- \quad \url{http://www.math.utk.edu/~swise/Site/BSAM.html}
%

	\smallskip
	
{\LARGE\bf Service}
	\begin{description}
	\item
{\Large\bf University}
	\begin{description}
	\item
\textbf{Electrical Engineering and Computer Science (EECS) Department External Review Committee}, Office of the Provost, UTK, Spring 2019.
	\end{description}


	\item
{\Large\bf College of Arts and Sciences}
	\begin{description}
	\item
\textbf{Connections and Global Challenges Curriculum Committee}, UTK, 2016-17, 2017-18, 2018-19.
	\end{description}
	
	\item
{\Large\bf Department}
    \begin{description}
    \item
\textbf{Advisory Committee}, UTK, academic years 2011-12, 2012-13, 2014-15, 2015-16, 2018-19 (elected member), 2019-20.
    \item
\textbf{Assistantship Committee}, UTK, academic years 2012-13, 2017-18.
    \item
\textbf{Bylaws Committee}, UTK, academic year 2013-14.
	\item
\textbf{Colloquium Committee}, UTK, academic years 2007-08, 2008-09 (chair), 2009-10 (chair).
    \item
\textbf{Graduate Committee}, UTK, academic years 2007-08, 2008-09, 2009-10, 2010-11 (chair), 2011-12 (chair), 2015-16, 2016-17, 2018-19 (chair, Spring 2019), 2020-21, 2022-23 (chair).
    \item
\textbf{High School Math Contest}, UTK, timer (2007, 08, 10, 11, 14), judge, (2009, 11, 12, 13, 15).
%    \item
%\textbf{Mathematics Department Soccer Club Organizer/Advisor}, UTK, January 2010 - present.
    \item
\textbf{NIMBioS Mentor}, UTK. REU: summers 2009 and 2010; Postdoc: Sharon Bewick, August 2009 - May 2011; GRA Advisor: Tri Sri Noor Asih, August 2013 - May 2014.
	\item
\textbf{M.S. Examination Committees}, UTK, Robert Burnham, Summer 2011; Aaron Craig, Fall 2014; Steve Fassino, Summer 2013; Stephen E. Galloway, Spring 2017 (primary advisor); Casey Hufford, Summer 2011; Dragos Ilas, Fall 2013; Kai Kang, Spring 2012 (primary advisor); Manda Saylor, Spring 2010; Jillian Trask, Summer 2014.
	\item
\textbf{Ph.D. Examination Committees}, UTK, Andreas Aristotelous, Summer 2011 (co-advisor with O.~Karakashian); Yang Bai, Spring 2011 (Computer Science); Kylie Berry, Summer 2019 (co-advisor with T.~Mengesha); Holly Clark,  Spring 2014; Craig Collins, Summer 2015 (co-advisor with O.~Karakashian); Nick Dexter, Summer 2018; Amanda Diegel, Spring 2015 (primary advisor); Khoa Dinh, Summer 2019; Stephen Galloway, Summer 2020 (primary advisor); Kyle Golenbiewski Spring 2016; Zhen Guan, Summer 2012 (primary advisor); Peter Jantsch, Summer 2017; Tim Krumwiede, Fall 2016; Cody Lorton, Summer 2014; Hamza Ruzayqat, Spring 2019; Mikhail Sekachev, Summer 2013 (Mechanical Engineering); Miun Yoon, Fall 2010.
	\item
\textbf{Search Committees}, UTK, academic years 2008-09 (JICS), 2011-12 (PDE), 2012-2013 (Computational and Applied Mathematics), 2016-2017 (Math Biology), 2022-23 (Math Biology).
	\item
\textbf{Tenure and Promotion (T\&P) and Promotion (P) Committees}, UTK, academic year 2016-17 (A.~Salgado, T\&P), 2017-18 (T.~Mengesha, T\&P), 2020-21 (A.~Salgado, P), 2021-22 (T.~Mengesha, P), 2021-22 (O.~Prosper, T\&P).

	\item
\textbf{First-Year Graduate Advising Committee}, UTK, 2022-23.


    \end{description}
    \item
{\Large\bf Community}
    \begin{description}
    \item
\textbf{Associate Editor},  Discrete and Continuous Dynamical Systems, Series S (DCDS-S), 2014-present.
	\item
\textbf{Associate Editor}, Advances in Applied Mathematics and Mechanics (AAMM), 2018 - present.
	\item
\textbf{Associate Editor}, Numerical Mathematics: Theory, Methods and Applications (NMTMA), 2017 - present.
    \item
\textbf{Advisory Editor/Communicator}, Mathematical Methods in the Applied Sciences (MMAS), 2014-2019.
    \item
\textbf{Journal Reviewer}, Acta Materialia, Applied Mathematics and Computation, Applied Numerical Mathematics, Communications in Computational Physics, Communications in Mathematical Sciences, Discrete and Continuous Dynamical Systems B, IMA Journal of Applied Mathematics, Journal of Computational Physics, Journal of Crystal Growth, Mathematical Biosciences and Engineering, Mathematics of Computation, Physical Review E, Polymer Engineering and Science, SIAM Journal on Numerical Analysis, Science China Mathematics, Thin Solid Films.
    \item
\textbf{Mini Symposium Organizer}
	\begin{description}
	\item
Society for Industrial and Applied Mathematics (SIAM) Conference on Mathematical Aspects of Materials Science, May 2010: ``The Ubiquitous Nature of Instabilities During Step-Flow Epitaxy."
    \item
Society for Industrial and Applied Mathematics (SIAM) Conference on Mathematical Aspects of Materials Science, May 2010: ``Mathematical and Computational Advances in Phase Field Crystal Modeling."
    \item
International Congress of Industrial and Applied Mathematicians (ICIAM) 2011, July 2011: ``Theoretical, Mathematical, and Computational Aspects of Crystal Dynamics."
	\item
American Institute of Mathematical Sciences (AIMS), 9th International Conference On Dynamical Systems and Differential Equations, July 2012: ``Multiphase Flows in Porous Media and Related Systems."
    \item
Society for Industrial and Applied Mathematics (SIAM) Conference on Mathematical Aspects of Materials Science, June 2013: ``Phase Field Methods in Materials Science."
	\item
American Mathematical Society (AMS), Southeastern Spring Sectional Meeting, March 2014: ``Special Session on Scientific Computing, Numerical Analysis, and Mathematical Modeling."
	\item
American Institute of Mathematical Sciences (AIMS), 11th International Conference On Dynamical Systems and Differential Equations, July 2016: ``Computational Methods for Phase Field Methods."
    \item
Society for Industrial and Applied Mathematics (SIAM) Conference on Mathematical Aspects of Materials Science, May 2021: ``Bulk and Surface Diffusion in Structured Membranes."
	\end{description}
	\item
\textbf{NSF Panel Reviewer}, Computing and Communication Foundations, Division of Materials Research, Division of Mathematical Sciences.
	\item
\textbf{Workshop Organizer}, National Institute for Mathematical and Biological Synthesis (NIMBioS) Investigative Workshop ``Solid Tumor Modeling," Jan. 19-21, 2011.
	\item
\textbf{Steering Committee Member}, Southeastern-Atlantic Regional Conference on Differential Equations (SEARCDE), October 2010 - October 2014.
	\item
\textbf{Conference Co-Organizer} 
	\begin{description}
	\item 
Southeastern-Atlantic Regional Conference on Differential Equations (SEARCDE), with S.~Lenhart (UTK, lead) and T.~Phan (UTK), September 21, 22, 2013, Knoxville, TN.
	\item
2017 Barrett Lectures: Mathematical Foundations of Data Sciences, with V.~Maroulas (UTK, lead), C.~Webster (UTK), J. Rosinski (UTK), May 1, 2, 3, 2017, Knoxville, TN.
	\item
2019 SIAM-SEAS Conference, with C.~Webster (UTK, Lead), G.~Zhang (ORNL), September 20, 21, 22, 2019, Knoxville, TN.
	\end{description}
    \end{description}
    \end{description}
    
    \smallskip

{\LARGE\bf  Graduate Students}
	\begin{description}
	\item
{\Large\bf Former}
	\begin{description}
	\item
Andreas Aristotelous, Math UTK (primary advisor, O.~Karakashian), PhD August 2011.  Thesis:~``Adaptive Discontinuous Galerkin Finite Element Methods for a Diffuse Interface Model of Biological Growth."  First position: postdoc at Duke University and SAMSI.
	\item
Kylie Berry (co-advisor, Tadele Mengesha), Math UTK, PhD 2019.  Topic:~``Energy-Based Blending Models in Peri-dynamics."
	\item
Craig Collins (primary advisor, O.~Karakashian), Math UTK, PhD 2015.  Thesis:~``Domain Decomposition Methods for Discontinuous Galerkin Approximations of Elliptic Problems." First postion: Assistant Professor of Mathematics at Murray State University, Murray, KY.
	\item
John Cummings (co-advisor, Rajeev Kumar), Math UTK, PhD 2017.  Topic:~``Simulating Block Polymer-Solvent Mixtures for Organic-Photovoltaic Devices." First position: Visiting assistant professor, Berry College, Rome, GA.
	\item
Amanda Diegel, Math UTK, PhD May 2015.  Thesis:~``Numerical Analysis of Convex Splitting Schemes for Cahn-Hilliard and Coupled Cahn-Hilliard-Fluid-Flow Equations." First position: Postdoctoral researcher in Mathematics at  Louisiana State University, Baton Rouge, LA.
	\item
Wenqiang Feng  Math UTK, PhD 2017.  Topic:~``Linearly Preconditioned Nonlinear Solvers for Phase Field Equations Involving p-Laplacian Terms." First position: Data scientist, DST Systems Inc, Kansas City, MO. 
	\item
Stephen Galloway, Math UTK, MS 2017.  Project:~``Numerical Simulation of Solidification with Strong Interface Anisotropy." Continued in PhD program at UTK.
	\item
Stephen Galloway, Math UTK, PhD 2020.  Thesis:~``Graphene Formation using the PFC Model with a Vapor Phase." First position: Assistant Professor of Mathematics at St.~Andrews University, Laurinburg, NC.
	\item
Zhen Guan, Math UTK, PhD August 2012.  Thesis:~``Numerical Analysis of First and Second Order Unconditionally Energy Stable Schemes for Nonlocal Cahn-Hilliard and Allen-Cahn Equations." First position: Visiting Assistant Professor of Mathematics at the University of California, Irvine, CA.

	\item
Kai Kang, Math UTK, MS May 2012.  Project:~``A Second-Order Accurate Energy Stable Scheme for the Cahn-Hilliard-Hele-Shaw System of Equations: Application to Tumor Growth." Went on to complete PhD at UTK, 2017.

	\item
Jea-Hyun Park (co-advisor, Abner Salgado), Math UTK, PhD 2021.  Thesis:~``Preconditioned Nesterov's accelerated gradient descent method and its applications for nonlinear PDE." First position: Visiting Assistant Professor of Mathematics at the University of California, Santa Barbara, CA.
	\end{description}
	\item
{\Large\bf Current}
	\begin{description}	
	\item
Evan Habbershaw (co-advisor, Cory Hauck), Math UTK, PhD 2024 (expected).
	\item
Ben Plumridge (primary advisor, Cory Hauck), Math UTK, PhD 2024 (expected).
	\end{description}

	\end{description}

	\clearpage
	\newpage

{\LARGE\bf  References}
	
	\begin{multicols}{2}

	
	
	\begin{enumerate}
	\item
\textbf{Wenbin Chen,} Professor
	\\
School of Mathematics
	\\
Fudan University
	\\
Shanghai, China 200433
	\\
\url{wbchen@fudan.edu.cn}
	
	\item	
\textbf{Qiang Du,} Fu Foundation Professor of 
	\\
\hspace*{0.25in} Applied Mathematics
	\\
Department of Applied Mathematics
	\\
Columbia University
	\\
New York, NY 10027
	\\
\url{qd2125@columbia.edu}

%	\item
%\textbf{William C. Johnson,} Professor and Chair
%	\\
%Department of Materials Science and Engineering
%	\\
%PO Box 400745, 395 McCormick Road
%	\\
%University of Virginia
%	\\
%Charlottesville, VA 22904-4745
%	\\
%\url{wcj2c@virginia.edu}
%	\\
%434-982-4884

	\item
\textbf{John S. Lowengrub,} Chancellor's 
	\\
\hspace*{0.25in} Professor
	\\
Mathematics Department
 	\\
540H Rowland Hall
	\\
University of California
	\\
Irvine, CA 92697-3875
	\\
\url{jlowengr@uci.edu}

	\item
\textbf{Brian Wetton,} Professor
	\\
Mathematics Department
	\\
University of British Columbia 
	\\
Vancouver, BC, Canada V6T 1Z2
	\\
\url{wetton@math.ubc.ca}
	
	\columnbreak
	
	\item
\textbf{Keith Promislow,} Professor
	\\
Department of Mathematics
	\\
Michigan State University
	\\
East Lansing, MI 48864
	\\
\url{promislo@msu.edu}
	
	\item
\textbf{Jie Shen,} Professor
	\\
Department of Mathematics
	\\
Director, Center for Computational  
	\\
\hspace*{0.25in} and Applied Mathematics
	\\
Purdue University
	\\
West Lafayette, IN 47907
	\\
\url{shen7@purdue.edu}

 	\item
\textbf{Axel Voigt,} Professor and Director
	\\
Institut f\"{u}r Wissenschaftliches 
	\\
\hspace*{0.25in} Rechenen
	\\
Technische Universit\"{a}t Dresden
	\\
01062 Dresden, Germany
	\\
\url{axel.voigt@tu-dresden.de}
	
	\item
\textbf{Xiaoming Wang,} Professor and  
	\\
\hspace*{0.25in} Havener Department Chair
	\\
Department of Mathematics 
	\\
\hspace*{0.25in}and Statistics
	\\
Missouri University of Science and
	\\
\hspace*{0.25in} Technology
	\\
Rolla, MO 65409-0020
	\\
\url{xiaomingwang@mst.edu}

	\end{enumerate}
	
	\end{multicols}
	
    \end{document}
